Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-07-01 analysis/supplementary materials/Supplementary Materials.Rmd
Correct caption for figure S2

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:23, 1:20)]

>>>>

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:23, 1:20)]
